%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4
% Command for printing skill overview bubbles
\newcommand\skills{ 
~
	\smartdiagram[bubble diagram]{
        \textbf{Astronomer},
        \textbf{~~Bayesian~~}\\\textbf{~Statistics~},
        \textbf{~~Big Data~~},
        \textbf{~~Observer~~},
        \textbf{~~Numerical~}\\
        \textbf{~Techniques~}
    }
}

% Programming skill bars
\programming{{C $\textbullet$ C++  $\textbullet$ R $\textbullet$ Ruby $\textbullet$ IDL $\textbullet$ html / 2.5}, {Shell $\textbullet$ SQL $\textbullet$ Matlab $\textbullet$ \large \LaTeX  / 4}, {Python / 5.5}}

% Projects text
\education{
     \textbf{Ph.D., Astronomy} \\
 University of Hertfordshire, UK \\
 2015 - Present \\
 Expected completion: 2019\\

 \textbf{MPhys, Physics} \\
 Durham University, UK \\
 2010 - 2014 \\
 2:1 with Honours\\

}

\affiliations{
 Fellow of the Royal Astronomical Society, \textit{FRAS}\\
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Shaun C Read} % Your name
\cvjobtitle{Ph.D.~Student} % Job
% title/career

\cvlinkedin{}
\cvgithub{Shaun C Read}
\cvnumberphone{+44 7909975186} % Phone number
\cvsite{shaun.science} % Personal website
\cvmail{shaun.c.read@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar
 
%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Summary}
     About me

\section{Experience}

\begin{twenty} % Environment for a list with descriptions \twentyitem{<dates>}{<title>}{<location>}{<description>}
     \twentyitem{Oct 2015 -}{Present}{Ph.D.~student}{University of Hertfordshire}{Supervisor: Dr Daniel J.B. Smith}{Thesis: Measuring the Physical Properties of Distant Galaxies and Black
Holes in the Era of Surveys\vspace{4}\begin{itemize}
\tightlist
\item
  Studying the relation between the star-formation rate and radio
  luminosity of galaxies.
\item
  Using new photometric time-series techniques to estimate quasar
  black-hole masses using reverberation mapping.
\item
  Innovating new Bayesian methods to infer complete distributions from
  incomplete, noisy data in order to mitigate observational bias and
  explore large datasets.
\end{itemize}} \\
 \twentyitem{Jun 2016 -}{}{Observing}{William Herschel Telescope, La Palma}{}{\vspace{4}} \\
 \twentyitem{Jan 2016 -}{Present}{Programming teaching assistant \& tutor}{University of Hertfordshire, UK}{}{\vspace{4}\begin{itemize}
\tightlist
\item
  Taught students Python and Matlab for scientific programming courses.
\item
  Assisted students with programming exercises.
\item
  Lead programming lectures and demonstrations.
\end{itemize}} \\
 \twentyitem{Nov 2016 -}{Mar 2017}{`Physics of stars' demonstrator}{University of Hertfordshire, UK}{}{\vspace{4}\begin{itemize}
\tightlist
\item
  Assisted students at the Bayfordbury teaching observatory.
\item
  Instructed in the use of 16-inch telescopes and the reduction of data.
\item
  Projects included PNe imaging and constructing open cluster
  HR-diagrams.
\end{itemize}} \\
 \twentyitem{Jul 2014 -}{Jul 2015}{Insight Analyst}{Linkdex, UK}{Processing big data from raw consumer search patterns to an explanative
format suitable for client business strategies.}{\vspace{4}\begin{itemize}
\tightlist
\item
  Big data processing with Python \& sci-kit learn
\item
  Communication with the backend team
\item
  API design, visualisation, and automation development.
\end{itemize}} \\
 \twentyitem{Jun 2013 -}{Aug 2013}{Summer Student}{National Physical Laboratory, UK}{\textbf{Supervisor}: Dr Alastair Sinclair}{\vspace{4}\begin{itemize}
\tightlist
\item
  Worked with the Time \& Frequency Team.
\item
  Analysed Gaussian beam quality for the strontium ion optical clock
  group.
\item
  Developed analytical Matlab code and the optical bench setup required.
\end{itemize}} \\
\end{twenty}

%----------------------------------------------------------------------------------------
%	 RESEARCH
%----------------------------------------------------------------------------------------
\section{Research Interests}
\begin{itemize}
     \item \textbf{Star-formation}: LOFAR, FIR, empirical relations, FIRC, MagPhys, SFG-AGN interface.
 \item \textbf{Reverberation mapping}: High redshift, photometric techniques, $t_{lag}-L_{5100}$, selection
biases.
 \item \textbf{Big data \& Bayesian analysis}: Large surveys, advanced Bayesian statistical inference, bias mitigation.
\end{itemize}

\newpage
\newgeometry{left=2cm,top=2cm,nohead,nofoot}
\section{Publications}
\subsection{Published}
\begin{itemize}
     \item \textit{The Far-Infrared Radio Correlation at low radio frequency with
LOFAR/H-ATLAS}, \textbf{Read, S. C.}; Smith, D. J. B.; Gürkan, G.; Hardcastle, M. J.;
Williams, W. L.; Best, P. N.; Brinks, E.; Calistro-Rivera, G.; ChyŻy, K.
T.; Duncan, K.; Dunne, L.; Jarvis, M. J.; Morabito, L. K.; Prandoni, I.;
Röttgering, H. J. A.; Sabater, J.; Viaene, S. -- 2018MNRAS.480.5625R\\
 \item \textit{LOFAR/H-ATLAS: a deep low-frequency survey of the Herschel-ATLAS North
Galactic Pole field}, Hardcastle, M. J.; Gürkan, G.; van Weeren, R. J.; Williams, W. L.; Best,
P. N.; de Gasperin, F.; Rafferty, D. A.; \textbf{Read, S. C.}; Sabater,
J.; Shimwell, T. W.; Smith, D. J. B.; Tasse, C.; Bourne, N.; Brienza,
M.; Brüggen, M.; Brunetti, G.; Chyży, K. T.; Conway, J.; Dunne, L.;
Eales, S. A.; Maddox, S. J.; Jarvis, M. J.; Mahony, E. K.; Morganti, R.;
Prandoni, I.; Röttgering, H. J. A.; Valiante, E.; White, G. J. -- 2016MNRAS.462.1910H\\
\end{itemize}

\subsection{Submitted and in preparation}
\begin{itemize}
     \item \textit{Highly Efficient Photometric Reverberation Mapping at High Redshift}, Read, S.C. Smith, D. J. B. Jarvis, M. J. Gürkan, G. -- submitted to MNRAS\\
 \item \textit{On the Causes of the Mass Dependency of the Star-formation Rate -- Radio
Luminosity Relation with LOFAR, Horizon-AGN, and CANDID}, Read, S.C. Smith, D. J. B. Gürkan, G. Hardcastle, M. J. et al. -- in prep.\\
 \item \textit{A LOFAR-IRAS cross-match study: the far-infrared radio correlation and
the 150 MHz luminosity as a star-formation rate tracer}, Wang, L. Rowan-Robinson, M. Gao, F. Bonato, M. Calistro-Rivera, G.
Chyży, K.T. Duncan, K.J. Farrah, D. Gurkan, G. Hardcastle, M.J.
McCheyne, I. Prandoni, I. Read, S.C. Röttgering, H.J.A. Sabater, J.
Shimwell, T. W. Smith, D.J.B. Williams, W.L. -- in prep.\\
 \item \textit{Bias and Accretion Rate Dependency in the Reverberation-Mapped
Lag-luminosity Relation}, Read, S.C. Smith, D. J. B. et al. -- in prep.\\
 \item \textit{Galaxy Morphological Classification in Deep-Wide Surveys via
Unsupervised Machine Learning}, Martin, G. Kaviraj, S. Hocking, A. Read, S.C. Geach, J. -- in prep.\\
 \item \textit{Brown dwarfs with Gaia}, Gonzalez, E. Pinfield, D. Read, S.C. et al. -- in prep.\\
\end{itemize}

\section{Presentations}
\begin{twenty}
     \twentyitem{April 2018}{}{European Week of Astronomy and Space Science}{European Astronomical Society, \emph{EAS}}{University of Liverpool, UK}{poster}\\
 \twentyitem{July 2017}{}{National Astronomy Meeting}{Royal Astronomical Society, \emph{RAS}}{University of Hull, UK}{contributed talk}\\
 \twentyitem{June 2016}{}{National Astronomy Meeting}{Royal Astronomical Society, \emph{RAS}}{University of Nottingham, UK}{contributed talk, poster}\\
 \twentyitem{May 2016}{}{The Cosmic FIR Landscape with H-ATLAS}{H-ATLAS consortium}{University of Lisbon, Portugal}{contributed talk}\\
\end{twenty}

\end{document} 